\documentclass{ExpressiveCoverLetter}

\begin{document}

\coverletterheader[
    firstname=Artur,
    % middleinitial=N,
    lastname=Sogomonyan,
    email=arthur.sogomonyan@gmail.com,
    phone=+43 677 64114581,
    linkedin=artur-sogomonyan,
    github=PropovedNik007,
    website=arterra,
    city=Vienna,
    state=Austria
]

\vspace{0.25in}
\today
\vspace{0.15in}

Dear Hiring Team at contextflow,

I am excited to apply for the (Junior) Machine Learning Developer position. With a Master’s in Data Science from TU Wien and hands-on experience in machine learning and medical imaging, I am eager to contribute to your mission of supporting radiologists with AI-powered tools.

In my role at TU Wien’s Rail4Future project, I optimized LSTM models for Siemens and ÖBB, ensuring robust performance. At GLOSAV, I developed a real-time object detection algorithm using YOLOv5, achieving sub-5ms latency. Additionally, I built scalable pipelines integrating OCR, NER, and deep learning models like LLaMA-3 in projects such as susteam.

I am skilled in Python, PyTorch, and cloud tools (AWS) with a structured work style and a strong belief in teamwork. My experience with MLOps, DICOM, and medical workflows positions me to make an immediate impact at contextflow.

I would welcome the opportunity to contribute to a product that improves patient care while growing within your interdisciplinary team. I look forward to discussing how my experience aligns with your needs.

Best regards,

\vspace{.01in}

Artur Sogomonyan

\end{document}