\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Artur,
    % middleinitial=,
    lastname=Sogomonyan,
    email=arthur.sogomonyan@gmail.com,
    phone= +43-677-641-145-81,
    linkedin=artur-sogomonyan,
    github=PropovedNik007,
    website=arterra,
    city=Vienna,
    state=Austria,
    qrcode=demo.jpg,
    fixobjectivespacing=false
]

% \objective{Machine Learning Engineer}

\section{Professional Summary}
\noindent Visionary AI Engineer and CTO with expertise in building end-to-end intelligent systems that bridge physical and digital worlds. Specialized in deploying production-ready AI solutions across sustainable technology, autonomous transportation, and decentralized systems. Proven track record of translating complex business problems into scalable technical architectures using cutting-edge Machine Learning, Computer Vision, and LLMs.

% ----- Education -----
\section{Education}

\experience{Master of Science}{Data Science}{2022}{2025}{
    \noindent Technische Universität Wien, Austria
}

\experience{Bachelor of Science}{Information technologies and
telecommunications}{2014}{2020}{
    \noindent Bauman Moscow State Technical University \newline
    Diploma thesis ``3D printer failure detection system based on computer vision detection"
}

% ----- Work Experience -----
\section{Work Experience}

\experience{susteam}{CTO \& Data Scientist}{Jan 2023}{Feb 2025}{
    \achievement{Architected and built automated ESG analytics platform from scratch, engineering multi-stage pipeline with OCR and RAG-augmented LLMs for greenwashing detection}
    \achievement{Developed a full-stack solution of scalable AWS microservices architecture with React frontend, increasing data processing throughput by 60\%}
    \achievement{Delivered market-ready product automating sustainability reporting for hospitality clients, providing explainable AI-driven insights}
    \tech{FastAPI, AWS, React, OCR, LangChain, BERT, LLaMA3, RAG}
}

\experience{Technische Universität Wien}{Research Scientist — Rail4Future}{Feb 2024}{Jul 2024}{
    \achievement{Optimized LSTM-based digital twin for rail infrastructure, improving prediction accuracy by 27\% and reducing training time by 40\% for Siemens and ÖBB}
    \achievement{Implemented rigorous statistical validation frameworks establishing new standards for model robustness in production}
    \achievement{Refactored and modularized codebase enabling faster experimentation cycles and reliable deployment}
    \tech{Python, TensorFlow, LSTM, Statistical Analysis, Digital Twins}
}

\experience{GLOSAV}{Machine Learning Analyst}{Feb 2021}{Jul 2021}{
    \achievement{Developed a computer vision pipeline for obstacle detection and tracking on railway routes using YOLOv5 and OpenCV.}
    \achievement{Achieved sub-5ms latency on real-time streams by optimizing frame processing and inference pipelines.}
    \achievement{Enhanced detection stability through custom temporal smoothing and calibration algorithms.}
    \tech{Python, YOLOv5, OpenCV, NumPy}
}

\experience{Arterra Miniature}{Software Engineer \& 3D Maker}{Feb 2020}{Mar 2021}{
    \achievement{Created interactive 3D visualizations and prototypes, delivering end-to-end custom hardware and software solutions for clients.}
    \achievement{Integrated microcontrollers and designed automation for small-scale production devices and art installations.}
    \tech{Blender, Cura, Arduino, Python}
}

\experience{Full-Stack Developer}{Freelance \& Linwood}{Mar 2017}{Sep 2019}{
    \achievement{Designed, implemented, and deployed full-stack web applications for e-commerce and educational platforms.}
    \achievement{Optimized page load times and database queries, improving performance by up to 40\%.}
    \achievement{Delivered complete front-end redesigns and backend extensions for clients using modern frameworks.}
    \tech{Python, Django, PHP, Yii2, React, JavaScript, HTML/SCSS, PostgreSQL}
}

\experience{KRK Group}{Frontend Developer}{Sep 2019}{Dec 2019}{
    \achievement{Implemented user interfaces and database communication for an internal learning platform.}
    \achievement{Collaborated with backend developers to ensure responsive, accessible, and scalable front-end components.}
    \tech{React, JavaScript, REST APIs}
}


% ----- Skills -----
% \section{Skills}
% \noindent\begin{tabularx}{\textwidth}{@{}X@{}X@{}X@{}X@{}}
% \textbf{Software Development}
% \begin{itemize}
%     \item Docker, Git
%     \item Python, C++, R
%     \item Django, Flask, FastAPI
%     \item JavaScript, TypeScript
%     \item React, Svelte
% \end{itemize}
% &
% \textbf{Machine Learning}
% \begin{itemize}
%     \item scikit-learn 
%     \item Pandas, NumPy
%     \item Tensorflow, PyTorch
%     \item OpenCV, YOLO
%     \item NLTK, SpaCy
%     \item Bert, LLama3, GPT
%     \item LangChain, LlamaIndex
%     \item Anthropic agents, MCP
% \end{itemize}
% &
% \textbf{Databases and Cloud}
% \begin{itemize}
%     \item PostgreSQL
%     \item MongoDB
%     \item Redis
%     \item RabbitMQ
%     \item nginx, Gunicorn
%     \item Spark
%     \item AWS EC2, S3
%     \item Linux/Debian/Fedora
% \end{itemize}
% &
% \textbf{Languages}
% \begin{itemize}
%     \item English (C1)
%     \item German (A2)
%     \item Russian (C2)
%     \item Armenian (B2)
% \end{itemize}
% \end{tabularx}

% ----- Technical Projects -----
% \section{Technical Projects}

% \experience{Expressive Resume}{Personal Project}{Nov 2021}{Dec 2021}{
%     \achievement{

%         Created a \tech{\LaTeX} class that makes it easy for anyone to quickly create a beautiful resume and cover letter.

%     }
% }

% ----- Projects -----
\section{Projects}

\experience{Full-stack and Machine Learning Development}
{LawSyncr}{Aug 2024}{}
{
    \achievement{
    Conducted in-depth research and analysis to evaluate innovative ideas, leading to the creation of a comprehensive pitch deck.
    }
    \achievement{
    Led the end-to-end full-stack development of the project, including the implementation of a Minimum Viable Product (MVP) with integrated machine learning components.
    }
    \tech{Flask, Svelte, RAG, LLM}
}

\experience{Portfolio Website Development}
{Arterra}{Aug 2024}{}
{
    \achievement{
    Designed and developed a portfolio website, integrating CI/CD pipelines for seamless updates via GitHub Pages.
    }
    \achievement{
    Utilized Obsidian vault data to create an interactive front-end that visualizes my professional journey using graphology and sigma libraries.
    }
    \tech{Svelte, graphology, sigma}
}

\experience{Crypto Trading Analysis and Future Trading}
{TradeBot}{Jun 2024}{}
{
    \achievement{
    Engineered a bot to systematically scrape and collect trade data from Binance, allowing detailed real-time market analysis.
    }
    \achievement{
    Designed and implemented a robust trading strategy, optimizing both short-term gains and long-term trends.
    }
    \tech{asyncio, FastAPI, BinanceAPI, pandas, mplfinance}
}

\experience{Document Analysis and Optical Character Recognition (OCR)}
{DAVU Project TU Wien}{Jun 2024}{}
{
    \achievement{
    Conducted layout analysis of historical documents to improve text extraction accuracy.
    }
    \achievement{
    Integrated NER and fine-tuned LLaMA-3 for metadata extraction, enhancing accuracy in identifying dates, locations, and photographers.
    }
    \tech{Tesseract, SpaCy, LLaMA-3, Python}
}

\experience{Full-stack Development of NFT Platform}
{Cryptex}{Feb 2024}{}
{
    \achievement{
    Implemented a secure authentication system using MetaMask and Polygon blockchain for managing encoded NFTs.
    }
    \tech{Svelte, Polygon, Solidity}
}

\experience{Lip Reading App at Hackathon}
{Coding Austria}{Jul 2023}{}
{
    \achievement{
    Built a lips-reading app using the AV-HuBERT model for the Austrian Red Cross challenge, enabling communication in noisy environments.
    }
    \tech{AV-HuBERT, FastAPI, Next.js}
}

% ----- Awards -----
\section{Awards}

\experience{1st Place Winner}
{AI Mission Hackathon 3 — “Nightwalkers”}{Oct 2025}{}
{
    \achievement{
    Won 1st place by developing a sophisticated multi-tool AI agent that autonomously answered complex sustainability questions, achieving over 70\% accuracy on database and Wikipedia queries through iterative testing and prompt refinement.
    }
    \achievement{
    Architected a robust agentic system with five custom MCP servers for SQL databases, Wikipedia, PDF retrieval, currency conversion, and a Python-powered calculator to ensure precise arithmetic and data handling.
    }
    \achievement{
    Engineered a battle-tested Q&A system, which not only retrieves answers, but provides the sources (links, pages, database)
    }
    \tech{Claude Sonnet, Python, Model Context Protocol (MCP), SQL, FastMCP, Ragie, Wikipedia API}
}

\experience{2nd Place Winner} 
{AIM Hackathon — TIMETOACT Group}{Oct 2024}{}
{
    \achievement{
    Developed a Retrieval-Augmented Generation (RAG) platform to identify greenwashing in ESG reports, assigning trustworthiness scores and providing explainable insights.
    }
    \tech{LangChain, OpenAI, FAISS, Python, Flask}
}

\experience{2nd Place Winner}
{Tourism Technology Hackathon}{Nov 2023}{}
{
    \achievement{
    Created an interactive knowledge graph and chatbot that analyzes tourism data and visualizes points of interest on a map.
    }
    \tech{Selenium, GeoPandas, Folium}
}


\section{Studies and Publications}
\experience{IEEM24-F-0298}{Publication}{2024}{}
{
\noindent Comparative Analysis of Machine Learning-based Surrogate Modeling Approaches for Multi-body Dynamic Simulation in Railway Digital Twin Platform
}
% {
%     \noindent Presented at the International Conference on Industrial Engineering and Engineering Management (IEEM 2024). The paper discusses various machine learning surrogate models to enhance the efficiency of multi-body dynamic simulations, specifically applied to a railway digital twin platform.
% }


\experience{Deep Learning School}{Moscow Institute of Physics and Technology}{2020}{2021}

\experience{School of Data Analysis}{Higher School of Economics University and Yandex}{2020}{2020}


\section{Technical Skills}
\begin{tabularx}{\textwidth}{@{}>{\bfseries}l X@{}}
AI/ML:        & Python, TensorFlow, PyTorch, LLMs (BERT, LLaMA, GPT), RAG, LangChain, Computer Vision (YOLO, OpenCV), scikit-learn, Pandas, NumPy \\
Engineering:  & FastAPI, Django, React, Svelte, JavaScript/TypeScript, Docker, AWS (EC2/S3), PostgreSQL, Redis, RabbitMQ, Linux \\
Languages:    & English (C1), Russian (C2), Armenian (B2), German (A2) \\
\end{tabularx}

\end{document}