\documentclass{ExpressiveResume}

% ----- Resume -----
\begin{document}

% ----- Name + Contact Information -----
\resumeheader[
    firstname=Artur,
    % middleinitial=,
    lastname=Sogomonyan,
    email=arthur.sogomonyan@gmail.com,
    phone= +43-677-641-145-81,
    linkedin=artur-sogomonyan,
    github=PropovedNik007,
    website=arterra
    city=Vienna,
    state=Austria,
    qrcode=demo.jpg,
    fixobjectivespacing=false
]

% \objective{Machine Learning Engineer}

% ----- Education -----
\section{Education}

\experience{Master of Science}{Data Science}{2022}{now}{
    \noindent Technische Universität Wien, Austria
}

\experience{Bachelor of Science}{Information technologies and
telecommunications}{2014}{2020}{
    \noindent Bauman Moscow State Technical University \newline
    Diploma thesis "3D printer failure detection system based on computer vision detection"
}

% ----- Work Experience -----
\section{Work Experience}

\experience{Technische Universität Wien}
{Data Scientist in Project Rail4Future}
{Feb 2024}{Jul 2024}
{
    \achievement{
    Analyzing rail irregularities, refactoring and optimization of the LSTM models. Working with industrial partners Siemens and ÖBB.
    }
    \achievement{
    Performed significance tests, achieved robustness, and dramatically improved the performance of the model.
    }
}

\experience{susteam}{CTO, Data Scientist}{Jan 2023}{present}
{
    \achievement{
    Architecture and Full Stack development of the ESG system.
    }
    \achievement{
    Developed a pipeline with OCR, information retrieval, Data Analysis and Machine Learning. RAG implementation for LLMs.}
    
    \tech{
    FastAPI, Amazon Web Services (AWS), Amazon EC2, S3, React.js, Bert, LLama3
    }
}

\experience{GLOSAV}{Machine learning analyst}{Feb 2021}{Jul 2021}{
    \achievement{
    Engineered a sophisticated algorithm to detect railway routes with object detection and tracking mechanisms. Developed a robust way to track obstacles on the rails. Achieved good performance and latency for real-time stream less than 5ms.
    }
    \achievement{
    Contributed to the design and implementation of an expansive microservice architecture of the train autopilot system.
    }

    \tech{
    Python, YOLOv5, OpenCV, NumPy
    }
}

\experience{Arterra Miniature}{Project Manager, 3D-Modeller, Software Engineer}{Feb 2020}{Mar 2021}{
    \achievement{
    Working with customers, 3D visualization, prototyping, 3D printing, programming microprocessors and microcontrollers, work from scratch to delivery of projects.
    }
    
    \tech{
    Blender, Cura, Arduino
    }
}

\experience{KRK Group}{Frontend Developer}{Sep 2019}{Dec 2019}{
    \achievement{
    Developed corporate educational platform, React application, implementation of user interface, communication with databases.
    }

    \tech{
    JavaScript, React
    }
}

\experience{Linwood}{Full-Stack Developer}{Aug 2018}{Sep 2019}{
    \achievement{
    Implemented all stages of the online store development, subsequent testing, promotion and expansion of functionality for the required business tasks.
    }
}

\experience{Freelance}{Web developer}{Mar 2017}{Aug 2018}{
    \achievement{
    Carried out projects, as Front-end and Back-end. Implemented from scratch or refactored existing solutions for functionality extensions.
    }
    
    \tech{
    PHP, Yii2, html, scss, Python, Django
    }
    
}


% ----- Skills -----
\section{Skills}
\noindent\begin{tabularx}{\textwidth}{@{}X@{}X@{}X@{}X@{}}
\textbf{Software Development}
\begin{itemize}
    \item docker
    \item Python
    \item C++
    \item R
    \item Django
    \item Flask
    \item FastAPI
    \item JavaScript
    \item React, Svelte
\end{itemize}
&
\textbf{Machine Learning}
\begin{itemize}
    \item scikit-learn
    \item Pandas
    \item NumPy
    \item Tensorflow
    \item PyTorch
    \item OpenCV
    \item YOLO
    \item NLTK, SpaCy
    \item Bert, LLama3, GPT
\end{itemize}
&
\textbf{Databases and Cloud}
\begin{itemize}
    \item Git
    \item PostgreSQL
    \item MongoDB
    \item Redis
    \item RabbitMQ
    \item nginx, Gunicorn
    \item Spark
    \item AWS EC2, S3
    \item Linux/Debian/Fedora
\end{itemize}
&
\textbf{Languages}
\begin{itemize}
    \item English (C1)
    \item German (A2)
    \item Russian (C2)
    \item Armenian (B2)
\end{itemize}
\end{tabularx}

% ----- Technical Projects -----
% \section{Technical Projects}

% \experience{Expressive Resume}{Personal Project}{Nov 2021}{Dec 2021}{
%     \achievement{

%         Created a \tech{\LaTeX} class that makes it easy for anyone to quickly create a beautiful resume and cover letter.

%     }
% }

% ----- Projects and Awards -----
\section{Projects and Awards}

\experience{2nd Place Winner} 
{AIM Hackathon - TIMETOACT Group}{Oct 2024}{} 
{ 
    \achievement{ 
    Developed a platform that uses Retrieval-Augmented Generation (RAG) to identify greenwashing in ESG reports. The system analyzed text from ESG reports, matched it with labeled data on greenwashing indicators, and provided a score based on the trustworthiness of the content. I also integrated an explainability feature to retrieve the most relevant quotes for identified greenwashing examples. 
    } 
    \tech{ 
    LangChain, OpenAI, FAISS, Python, Flask 
    } 
}


\experience{Full-stack and Machine Learning Development}
{LawSyncr}{Aug 2024}{}
{
    \achievement{
    Conducted in-depth research and analysis to evaluate innovative ideas, leading to the creation of a comprehensive pitch deck.
    }
    \achievement{
    Led the end-to-end full-stack development of the project, including the implementation of a Minimum Viable Product (MVP) with integrated machine learning components.
    }
    
    \tech{Flask, Svelte, RAG, LLM}
}


\experience{Portfolio Website Development}
{Arterra}{Aug 2024}{}
    {
    \achievement{
    Designed and developed a portfolio website, integrating continuous integration/continuous deployment (CI/CD) pipelines for seamless updates via GitHub Pages.
    }
    \achievement{
    Utilized Obsidian vault data to create an interactive front-end that visualizes my professional journey using graphology and sigma libraries.
    }
    
    \tech{Svelte, graphology, sigma}
}

\experience{Crypto Trading Analysis and Future Trading}
{TradeBot}{June 2024}{}
{
    \achievement{
    Engineered a bot to systematically scrape and collect trade data from Binance, allowing detailed real-time market analysis.
    }
    \achievement{
    Designed and implemented a robust trading strategy, optimizing both short-term gains and long-term trends.
    }
    \achievement{
    Automated the execution of trading strategies using a custom built bot, ensuring consistent and timely trades.
    }
    
    \tech{asyncio, FastAPI, BinanceAPI, pandas, mplfinance}
}

\experience{Document Analysis and Optical Character Recognition (OCR)}
{DAVU Project TU Wien}{June 2024}{}
{
    \achievement{
    Conducted a comprehensive layout analysis of historical documents, identifying key structural elements to improve text extraction accuracy.
    }
    \achievement{
    Implemented an OCR pipeline using Tesseract, optimizing the process by experimenting with different binarization techniques, which resulted in significant improvements in Word Error Rate (WER) and Character Error Rate (CER).
    }
    \achievement{
    Analyzed the impact of various preprocessing methods, such as binarization and cropping, on OCR performance, achieving optimal text recognition by fine-tuning OCR engine parameters.
    }
    \achievement{
    Integrated advanced Named Entity Recognition (NER) using SpaCy and fine-tuned language models (e.g., LLaMA-3) to extract metadata from images, enhancing the accuracy of location, date, and photographer identification in historical datasets.
    }
    
    \tech{Tesseract, SpaCy, LLaMA-3, Python}
}

\experience{Full-stack Development of the NFT Platform}
{Cryptex}{Feb 2024}{}
{
    \achievement{
    Implemented a secure authentication system using MetaMask, which allows users to store and manage seed phrases as encoded NFTs.
    }
    \achievement{
    Developed the platform’s backend to interact seamlessly with the Polygon blockchain, ensuring efficient and secure transactions.
    }
    
    \tech{Svelte, Polygon, Solidity}
}



\experience{Lip Reading app at Hackathon}
{Coding Austria}{Jul 2023}{}
{
    \achievement{
    Utilized Audio-Visual Hidden Unit BERT model for lips reading task for the Austrian Red Cross challenge.
    }
    \achievement{
    Integrated the model into the web app, passing the video stream from the smartphone to the model, reading the lips and generating a text passed as a message to the chat.
    }
    \achievement{
    This application allowed the Red Cross team to communicate in a very noisy environment, when it is not possible to use walkie-talkies. 
    }

    \tech{AV-HuBERT, FastAPI, Next.js}
}


\experience{2nd Place Winner}
{Tourism Technology Hackathon}{Nov 2023}{}
{
    \achievement{
    Implemented a data pipeline mapping data from different sources and building a knowledge graph for different tourism subjects. The result I visualized as an interactive map with the chat bot, that could wrangle the the point of interest and conclude the insights of the analysis.
    }
    \tech{
    Selenium, geoandas, folium
    }
}

\section{Studies and Publications}
\experience{IEEM24-F-0298}{Publication}{2024}{}
{
\noindent Comparative Analysis of Machine Learning-based Surrogate Modeling Approaches for Multi-body Dynamic Simulation in Railway Digital Twin Platform
}
% {
%     \noindent Presented at the International Conference on Industrial Engineering and Engineering Management (IEEM 2024). The paper discusses various machine learning surrogate models to enhance the efficiency of multi-body dynamic simulations, specifically applied to a railway digital twin platform.
% }


\experience{Deep Learning School}{Moscow Institute of Physics and Technology}{2020}{2021}

\experience{School of Data Analysis}{Higher School of Economics University and Yandex}{2020}{2020}

\end{document}